% !TEX program = xelatex
% ============================================================
%  Journal Paper
% ============================================================
\documentclass[a4paper,12pt]{article}


% ------------------ Essential packages ------------------
\usepackage{amsmath,amssymb,amsfonts}    % Math
\usepackage{graphicx}                    % Figures
\usepackage{booktabs}                    % Professional tables
\usepackage{geometry}                    % Page margins
\geometry{a4paper, margin=2.5cm}
\usepackage{indentfirst}                 % Indent first paragraph after section headings
\usepackage{microtype}                   % Micro-typography for better line breaking
\usepackage{bookmark}                    % PDF bookmarks
\usepackage{hyperref}                    % Hyperlinks
\hypersetup{hidelinks}

% ------------------ Citations ------------------
\usepackage[authoryear,round]{natbib}

% ------------------ Other useful packages ------------------
\usepackage{caption}                     % Figure/table captions
\usepackage{subcaption}                  % Sub-figures
\usepackage{enumitem}                    % Custom lists
\usepackage{xcolor}                      % Colors
\usepackage{cleveref}                    % Smart references (\cref)
\usepackage{tabularx}                    % Flexible table widths
\usepackage{array}                       % Table column definitions
\usepackage{makecell}                    % Multi-line table cells
\usepackage{multirow}                    % Multi-row table cells
\usepackage{pifont}                      % Symbols and dingbats
\usepackage{placeins}                    % Keep floats within their logical sections

% ------------------ Publication layout ------------------
\captionsetup{font=small,labelfont=bf,skip=6pt}
\setlength{\textfloatsep}{14pt plus 3pt minus 3pt}
\setlength{\floatsep}{10pt plus 2pt minus 2pt}
\renewcommand{\topfraction}{0.88}
\renewcommand{\bottomfraction}{0.72}
\renewcommand{\textfraction}{0.10}
\renewcommand{\floatpagefraction}{0.85}
\makeatletter
\setlength{\@fptop}{0pt}
\setlength{\@fpsep}{12pt}
\setlength{\@fpbot}{0pt plus 1fil}
\makeatother

% ------------------ Document info ------------------
\title{Closed-Loop LLM Agents for Multi-UAV Wildfire Rescue}
\author{Author One \\
        Department, Institution, City, Postal Code, Country \\
        \and
        Author Two \\
        Department, Institution, City, Postal Code, Country}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
Multi-UAV wildfire rescue requires closed-loop decisions that convert uncertain
observations into executable fleet actions and adapt to changing conditions. We
formulate wildfire rescue as a closed-loop decision problem spanning situation
understanding, resource-constrained planning, validation, and runtime
adaptation. Our modular large language model (LLM)-based agent framework
combines Vision Analysis, Mission Planning, Episodic and Lesson Memory
retrieval, independent Validation, and Runtime Replanning to generate and
repair multi-UAV missions.

We evaluate the framework in a real-UAV-informed AirSim suite with 80 fixed
evaluation episodes across four difficulty levels. Sensing, energy, payload, and
communication constraints are calibrated from a physical platform. Experiments
show that LLM-based agents enable closed-loop rescue decisions, with Memory and
Runtime Replanning becoming more important as mission complexity increases. A
fine-tuned Qwen3-8B planner retains 98.24\% of the Gemini~3.1~Pro teacher
planner's average performance while substantially reducing planning overhead.
These results support LLM agents as high-level decision components for adaptive
multi-UAV wildfire response. The implementation is available at
\url{https://github.com/tongsuhdyem/Pipeline}.

\noindent\textbf{Keywords:} multi-UAV wildfire response; LLM agents; compact LLM fine-tuning; closed-loop decision making; real-to-sim evaluation
\end{abstract}

% ============================================================
%  Main body (split into separate files via \input)
% ============================================================

\input{sections/01-introduction}
\input{sections/02-related-work}
\input{sections/03-system-overview}
\input{sections/04-evaluation-suite-design}
\input{sections/05-experiments}
\input{sections/06-conclusion}

% ============================================================
%  Bibliography
% ============================================================

\bibliographystyle{plainnat}
\bibliography{references}

% ============================================================
%  Appendix (optional)
% ============================================================
% \appendix
% \input{sections/appendix}

\end{document}
