% !TEX root = ../main.tex
\section{Introduction}

Wildfires threaten ecosystems, infrastructure, and human safety
\citep{bowman2020wildfire}. UAVs can rapidly observe hazardous and inaccessible
areas through flexible aerial sensing \citep{allan2022remote}, but operational
response requires more than aerial detection. Observations must be converted
into task zones, assigned across a resource-limited fleet, and revised as the
fire or UAV state changes. Multi-UAV wildfire rescue is therefore a closed-loop
decision problem rather than an isolated perception or path-planning task.

Existing work has advanced fire detection, aerial scene understanding, and
damage assessment, but transforming observations into coordinated response
actions remains challenging \citep{erdelj2017help}. A practical plan must
respect energy, payload, communication, safety, and priority constraints
\citep{floreano2015science}, while accommodating fire evolution, UAV faults,
and resource shortages. Large language models (LLMs) and multimodal LLMs offer
a flexible interface for connecting visual interpretation, task decomposition,
and high-level planning \citep{driess2023palme}. However, free-form generation
is insufficient for safety-critical missions: plans can violate fleet constraints
or become invalid when execution conditions change.

We formulate multi-UAV wildfire rescue as a decision chain from aerial
observation to fire-situation understanding, resource-constrained planning, and
runtime adaptation. Our modular system combines Vision Analysis, Mission
Planning, Semantic and Deterministic Validation, Episodic and Lesson Memory,
and Runtime Replanning. It converts aerial imagery into fire points and task
zones, generates an executable plan, and uses retrieved cases and lessons to
support initial planning and fault-driven repair.

To evaluate this capability, we construct a real-UAV-informed AirSim suite that
assesses understanding, constrained planning, and adaptation under runtime
perturbations. It calibrates observation, energy, payload, and communication
conditions from a real platform, organizes 80 fixed evaluation episodes into
four difficulty levels, and measures completion, response, mission time, event stability,
resource pressure, and coordination.

The main contributions of this work are summarized as follows:
\begin{enumerate}[leftmargin=1.6em,itemsep=2pt,topsep=3pt]
    \item We develop a modular LLM-based rescue system that integrates
    Vision Analysis, constrained multi-UAV Mission Planning, independent
    Validation, Episodic and Lesson Memory, and Runtime Replanning.
    \item We construct a real-UAV-informed AirSim evaluation suite with four
    difficulty levels and six mission-level metrics for end-to-end assessment
    under controlled operational pressure.
    \item We evaluate multiple foundation-model configurations, analyze the
    contributions of Validation, Memory, and Runtime Replanning, and assess
    whether a compact planner specialized with validated demonstrations can
    retain strong mission performance with lower planning overhead.
\end{enumerate}

\endinput
