% !TEX root = ../main.tex
\section{Related Work}

\subsection{UAV-based Wildfire Response}

UAVs provide a practical means of observing wildfires in hazardous and
difficult-to-access areas, but operational wildfire response requires more than
detecting fire in aerial imagery. It requires a decision chain that transforms
observations into a current representation of the incident, allocates limited
airborne resources to the resulting tasks, and updates the mission when the
environment or fleet state changes. Existing work has made substantial progress
on the individual stages of this chain, including aerial perception, active
situation monitoring, autonomous flight planning, and multi-UAV coordination.

At the perception stage, multimodal sensing improves the reliability of fire
observations under the visually challenging conditions common in wildfire
scenes. Thermal--RGB fusion has been used to detect fire and hotspots from UAV
imagery, reducing sensitivity to smoke and illumination variation
\citep{yuan2021uavfire}. Transformer-based aerial semantic segmentation further
supports the interpretation of burned regions, vegetation, and terrain
\citep{zhang2022uavtransformer}, while learning-based 3D reconstruction can
provide geometric environmental models for navigation and inspection
\citep{yang2022uav3dreconstruction}. These methods produce the visual and
spatial evidence needed for response, but their outputs must still be converted
into mission-level entities, such as fire points, task zones, and safety-relevant
context, before they can drive rescue actions.

Situation awareness and planning research addresses part of this conversion.
Autonomous exploration and mapping enable UAVs to update knowledge of unknown
or changing disaster environments \citep{popovic2021uavdisaster}; next-best-view
planning selects viewpoints that maximize information gain and reduces
observation uncertainty \citep{bircher2016nbv}. On the action side, deep
reinforcement learning has been applied to autonomous navigation in unknown
environments \citep{xiao2021uavrl}, and coverage path planning supports
large-area search and perimeter scanning \citep{yu2022coverageuav}. However,
these methods generally optimize sensing, navigation, or coverage as an
individual capability. They do not by themselves produce a fleet-level,
resource-constrained response plan that explicitly links evolving fire
information to task priorities, payload use, endurance, and execution status.

Multi-UAV methods extend decision making from a single vehicle to a team.
Multi-agent reinforcement learning has demonstrated cooperative navigation and
task allocation capabilities \citep{yang2023multiagentuav}, while the broader
disaster-response literature highlights the value of UAV support and
human--robot collaboration in search-and-rescue operations
\citep{waharte2021uavsar}. Nevertheless, wildfire response remains difficult
because fire evolution, communication changes, energy depletion, and vehicle
failures can invalidate an initially feasible allocation. The literature is
therefore still dominated by modular or open-loop solutions: perception,
mapping, path planning, and coordination are often evaluated separately. In
contrast, this work treats wildfire rescue as a closed-loop decision problem
from aerial observation to structured fire-situation understanding,
resource-constrained multi-UAV planning, validation, and local runtime
replanning. This formulation connects the outputs of perception to executable
team actions and preserves mission continuity under operational perturbations.

\subsection{LLM-Based Robotic Agents}

Large language models (LLMs) provide an increasingly capable interface between
high-level human intent and robot behavior. Rather than replacing low-level
perception or control modules, they are commonly used to interpret language,
decompose goals, select skills, and reason over structured observations. This
role is particularly relevant to wildfire response, where a decision system
must translate a changing fire situation and operational constraints into a
coherent fleet mission rather than execute a fixed motion policy.

Language grounding and hierarchical planning are central directions in this
area. SayCan combines language-model scoring with robot affordance estimates so
that high-level instructions are grounded in executable skills
\citep{ahn2022saycan}. Code as Policies uses language models to generate
programmatic control policies, providing a flexible mechanism for composing
robot behavior from functions and APIs \citep{liang2023codeaspolicies}.
Related design guidance has shown how ChatGPT can be used to generate robot
workflows while exposing tool descriptions and environmental constraints to the
model \citep{vemprala2023chatgptrobotics}. Together, these approaches show that
LLMs can support task decomposition and action sequencing, but they also make
clear that generated actions require grounding and external feasibility checks.

Embodied and multimodal models extend this reasoning interface to visual and
physical state. RT-1 learns vision-language-action policies from large-scale
real-robot data \citep{brohan2023rt1}, while PaLM-E incorporates visual inputs
and robot states into an embodied language model \citep{driess2023palme}.
Socratic Models further demonstrate zero-shot reasoning by composing
specialized vision and language models \citep{zeng2023socratic}. These methods
strengthen the connection between perception and action, yet they are generally
evaluated on individual robots and predefined manipulation or navigation tasks.
They do not directly address the resource-constrained allocation of dynamic,
interdependent tasks across a rescue fleet.

LLM-based agents have also explored closed-loop decision making through
environmental feedback, navigation, and experience reuse. Inner Monologue uses
language-based feedback to revise embodied plans \citep{huang2023innermonologue},
and LM-Nav combines large pretrained models with semantic waypoints for
open-world navigation \citep{shah2023lmnav}. Voyager couples an LLM agent with
an automatic curriculum and a growing skill library for open-ended exploration
\citep{wang2023voyager}. Nevertheless, these systems primarily target single-
agent embodied environments. In contrast, our system applies LLM reasoning to
multi-UAV wildfire response, coupling multimodal fire-situation understanding
with constrained fleet-level planning, independent Validation, Episodic and
Lesson Memory, and Runtime Replanning. The resulting design treats the LLM as a
high-level decision component within a closed-loop safety and execution
framework rather than as an unconstrained controller.

\endinput
