% !TEX root = ../main.tex
\section{Conclusion}

This paper studies multi-UAV forest-fire rescue as a closed-loop decision
problem that connects aerial situation understanding, resource-constrained
mission planning, and runtime adaptation. To represent this process, we
formulate the rescue workflow as the mappings from observations to fire points
and task zones, from task zones and fleet states to an initial plan, and from
runtime perturbations to a revised plan. Based on this formulation, we develop
a modular system that integrates Vision Analysis, Mission Planning, Validation, Runtime Replanning, and two forms of
experience memory. The resulting architecture produces executable fleet plans,
audits them before execution, and revises affected tasks when the operational
state changes.

We further introduce a real-UAV-informed evaluation suite in AirSim. The suite
uses platform and sensing constraints derived from a physical UAV and organizes
80 fixed episodes into four difficulty levels. Its mission-level metrics retain
separate views of task completion, response, mission time, event stability,
resource pressure, and coordination. Experiments with four foundation-model
configurations show that no single ranking holds across all conditions.
Gemini~3.1~Pro and Claude~Opus~4.7 perform strongly in the lower-difficulty
settings, whereas ChatGPT~5.5 achieves the highest scores in the hard and
expert settings. Across all models, increasing difficulty primarily degrades
time efficiency, coordination, and event stability rather than basic task
completion, identifying runtime continuity and time-aware resource allocation
as the main remaining bottlenecks.

The ablation results clarify the roles of the system components. Validation
produces a modest but consistent score improvement and is triggered across all
four difficulty levels, supporting its role as an occasional reliability
safeguard. Memory has limited influence in routine scenarios but becomes
increasingly important under resource and scheduling pressure, while removing
Runtime Replanning causes the largest degradation in hard and expert episodes.
The planner-specialization experiment additionally shows that validated
planning demonstrations can transfer domain behavior to a smaller model. On
the simple and normal episodes, the fine-tuned Qwen3-8B reaches 98.24\% of the
Gemini~3.1~Pro planner's average score, while reducing mean planning time from
37.50~s to 14.01~s and mean planning-token usage from 13,353 to 3,593. These
results demonstrate a practical path toward lower-cost local deployment of the
initial planning module.

Several limitations remain. The evaluation is conducted in a calibrated
simulation environment and therefore does not establish effectiveness in real
fire, smoke, weather, and communication conditions. The fixed episode set and
single platform calibration also cover only a limited range of possible fleet
scales and rescue environments. Moreover, the fine-tuned planner is evaluated
only in the simple and normal settings and does not yet replace the runtime
adaptation capability required by the complete closed loop. Future work will
extend the suite to real-flight and mixed real--sim trials, more diverse UAV
platforms and fire dynamics, and larger multi-UAV fleets. It will also examine
specialized models for hard and expert scenarios, more selective memory
retrieval, and replanning methods that improve mission continuity without
incurring excessive time and resource overhead.

\endinput
